Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2018-02-07 paper.tex
Update paper.tex

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods, has facilitated comprehensive study of introgression across a number of species (\textbf{Table 1}).
High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin and identify introgression across taxa \cite{Martin2015,Price2009,Lawson2012,pease2015,rosenzweig2016,geneva2015}.
The methods reviewed here do not include those marginally estimating introgression\slash migration rate as a component of demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and a series of methods utilizing the sequentially Markovian coalescent (PSMC, MSMC and SMC++) \cite{li2011, schiffels2014, terhorst2017}). 
Rather, we focus on methods that explicitly identify introgressed genomic segments based on the extent of differentiation, on patterns of nucleotide/haplotype sharing, and phylogenetic relationships.
%We focus here on analytical prospects and limitations and introduce only a few representatives of each category.

@@

Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role.
For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015});
introgression of wing coloration loci has conferred M\"{u}llerian mimicry
(a type of mimicry in which two unpalatable species resemble one another, compounding the efficacy of their repellant signal)
%\mbh{I would explain a bit more here...wing coloration loci, protects against predation...}
across butterfly species \cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.

@@

@@

After hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
%\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
%\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}
%Does one see different architectures of introgression across different regions?
%Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Introgressed regions are easier to detect when there has been limited recombination to break them apart.
Therefore, introgressions are easiest to detect when they are either recent (few generations means few recombination events) or involve structural variation (which diminishes recombination rate). \gmj{or when the introgressed region is nearer the centromere, where recombination is less common?}
Because recombination progressively breaks apart LD in introgressed regions, measurements of LD can be used to date introgression events (as in \cite{Poets2015}).

>>>>

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods, has facilitated comprehensive study of introgression across a number of species (\textbf{Table 1}). \gmj{Are there newer resequencing methods to discuss here?  DART-Seq, etc?}
High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin and identify introgression across taxa \cite{Martin2015,Price2009,Lawson2012,pease2015,rosenzweig2016,geneva2015}.
The methods reviewed here do not include those marginally estimating introgression\slash migration rate as a component of demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and a series of methods utilizing the sequentially Markovian coalescent (PSMC, MSMC and SMC++) \cite{li2011, schiffels2014, terhorst2017}). 
Rather, we focus on methods that explicitly identify introgressed genomic segments based on the extent of differentiation, on patterns of nucleotide/haplotype sharing, and phylogenetic relationships.
%We focus here on analytical prospects and limitations and introduce only a few representatives of each category.

@@

\gmj{This paragraph about application seems like it might not belong in this section.  Maybe it should be a part of the introduction?  Or, maybe each of these examples could be mentioned directly following the method(s) that was used in the study?}Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role.
For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015});
introgression of wing coloration loci has conferred M\"{u}llerian mimicry
(a type of mimicry in which two unpalatable species resemble one another, compounding the efficacy of their repellant signal)
%\mbh{I would explain a bit more here...wing coloration loci, protects against predation...}
across butterfly species \cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.

@@

\gmj{Li, can you update this section with your recent publication's findings?}

@@

After hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
%\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
%\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}
%Does one see different architectures of introgression across different regions?
%Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Introgressed regions are easier to detect when there has been limited recombination to break them apart.
Therefore, introgressions are easiest to detect when they are either recent (few generations means few recombination events) or involve structural variation (which diminishes recombination rate).
Because recombination progressively breaks apart LD in introgressed regions, measurements of LD can be used to date introgression events (as in \cite{Poets2015}).
